```{r}
setwd("D:/GA_SMART_COMMUNITIES_GRA/src/")
source("header_uli.R")

#functions
getValRange <- function(x, hilo) {
  ifelse(hilo %in% unlist(dimnames(x)), x["text",hilo][[1]], NA)
}

addZero <- function(x){
  for(i in 1:length(x)){
    if(as.integer(x[i]) <= 9){
      x[i] <- paste0("0",x[i])
    } else {
      x[i] <- x[i]
    }
  }
  
  return(x)
}
```


This grabs python data about the buildings

```{python}
import os
import osmnx as ox

path = "D:/GA_SMART_COMMUNITIES_GRA/src"
os.chdir(path)

pt = (41.91351,-87.66099)
dist = 1000

bldg = ox.buildings_from_point(pt, dist)

ox.save_gdf_shapefile(bldg, filename = "bldg_out", folder = "D:\GA_SMART_COMMUNITIES_GRA\src")

```

This section grabs zillow data
```{r}
set_zillow_web_service_id("X1-ZWz1gu2mdw56ob_8w9nb")

keeps <- c("addr_city","addr_count", "addr_house","addr_postc",
      "addr_stree", "amenity", "geometry")

csz = "Chicago, IL"

getValRange <- function(x, hilo) {
  ifelse(hilo %in% unlist(dimnames(x)), x["text",hilo][[1]], NA)
}

sdf <- st_read(dsn = "../src/bldg_out/bldg_out.shp", stringsAsFactors = FALSE) %>% select(one_of(keeps)) %>%
  filter(is.na(amenity) == TRUE) %>% filter(is.na(addr_house) == FALSE) %>%
  mutate(zillow_addr = paste(addr_house,addr_stree,sep = " "))

for(i in 1:nrow(sdf)) {
  if(i == 1){ remove(data)}
  
  xml <- GetSearchResults(address = sdf[i,]$zillow_addr, citystatezip = csz)
  
  if(length(xml$response[["results"]]) > 0){
    xmlDat <- xmlToList(xml$response[["results"]])
    
    out <- apply(xmlDat, MAR=2, function(property) {
      zpid <- property$zpid
      address <- unlist(property$address)
      z <- property$zestimate
      zestdf <- list(
        amount=ifelse("text" %in% names(z$amount), z$amount$text, NA),
        lastupdated=z$"last-updated",
        valueChange=ifelse(length(z$valueChange)==0, NA, z$valueChange),
        valueLow=getValRange(z$valuationRange, "low"),
        valueHigh=getValRange(z$valuationRange, "high"),
        percentile=z$percentile)
      list(id=zpid, address, zestdf)
    })
    
    if(is.data.frame(get("data")) == FALSE){
      data <- as.data.frame(do.call(rbind, lapply(out, unlist)), row.names = seq_len(length(out)))
    } else {
      data_temp <- as.data.frame(do.call(rbind, lapply(out, unlist)), row.names=seq_len(length(out)))
      data <- rbind(data,data_temp)
    }
    
  } else {}
}

summary(data$amount)